Recognizing Strong Gravitational Lenses

### 2015-02-17 doc/Milestone/milestone.tex

>>>>

We plan to train a classifier on this data using two different methods. First, we will code 
our own convolutional net in python using theano. Second, we will apply transfer learning 
techniques to train on a convolutional net galaxy morphology classifier, which has graciously 
been made available to us by Ryan Keisler and which achieved 7th place in the 2014 Galaxy 
Zoo Kaggle competition. This classifier runs $96\times96$ images through 3 convolutional 
layers and 2 fully-connected layers and predicts a galaxy to have one of 37 enumerated 
morphologies. We plan to train our classifier on top of the first full-connected layer, which 
has 500 neurons.
